---
title: "visiblespectrum Parameter Inputs"
output: rmarkdown::html_vignette
runtime: shiny
vignette: >
  %\VignetteIndexEntry{visiblespectrum Parameter Inputs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(dplyr)
library(kableExtra)
library(shiny)
library(gt)
library(flextable)
library(officer)
library(glitr)
knitr::opts_chunk$set(warning = FALSE)
```

```{r echo=FALSE}
load(system.file("extdata", "output.RData", package = "visiblespectrum"))
load(system.file("extdata", "ui_scrape.RData", package = "visiblespectrum"))
```

```{r results='asis'}
options_summary_df <- output$options_summary_df 

options_summary_df <- options_summary_df %>%
  mutate(
    parameter = recode(
      parameter,
      "ui_country" = "Countries",
      "ui_indicators" = "Indicators",
      "ui_ages" = "Age Categories",
      "ui_sexes" = "Sex Options",
      "ui_periods" = "Periods"
    )
  )

ui_scrape <- ui_scrape %>%
  mutate(
    ui_num_levels = ui_num_levels - 1 #area levels are 0 based, so go back 1
  )

parameters_by_country <- ui_scrape %>%
  rename(
    Country = ui_country,
    Indicators = ui_indicators,
    Ages = ui_ages,
    Sex_Options = ui_sexes,
    Periods = ui_periods,
    Max_Level = ui_num_levels
  ) %>%
  group_by(Country) %>%
  summarize(
    Indicators = as.character(paste(unique(unlist(Indicators)), collapse = ", ")),
    Ages = as.character(paste(unique(unlist(Ages)), collapse = ", ")),
    Sex_Options = as.character(paste(unique(unlist(Sex_Options)), collapse = ", ")),
    Periods = as.character(paste(unique(unlist(Periods)), collapse = ", ")),
    Max_Level = max(Max_Level)
  )
```

```{r}
ui <- fluidPage(
    tags$head(tags$style(HTML("
    .shiny-input-container {
      width: 300px;  /* Adjust width of input containers */
      height: 200px;
    }
    .downloadButton {
      width: 100%;  /* Make download buttons full width */
    }
  "))),
  downloadButton("downloadParameters", "Download Parameters by Country"),
  downloadButton("downloadAll", "Download All Parameters")
)

server <- function(input, output) {
  
  # Download handler for Parameters by Country
  output$downloadParameters <- downloadHandler(
    filename = function() {
      paste("parameters_by_country", ".csv", sep = "")
    },
    content = function(file) {
      write.csv(parameters_by_country, file, row.names = FALSE)
    }
  )

  # Download handler for All Parameters
  output$downloadAll <- downloadHandler(
    filename = function() {
      paste("all_parameters", ".csv", sep = "")
    },
    content = function(file) {
      write.csv(options_summary_df, file, row.names = FALSE)
    }
  )
}

# Run the app
shinyApp(ui = ui, server = server, options = list(height = 50))
```


### Input Parameters Summary

```{r echo=FALSE}
# Display the modified DataFrame
kable(options_summary_df)%>%
  kable_styling() %>%
  column_spec(1, bold = TRUE)

```
<details><summary><strong>For which parameters do most countries have data?</strong>
More than 90% of countries have data for these categories and are therefore referred to as <i>standard parameters</i>.</summary>
```{r echo=FALSE}
defaults_df <- output$defaults_df
defaults_df <- defaults_df %>%
    mutate(
    parameter = recode(
      parameter,
      "ui_country" = "Countries",
      "ui_indicators" = "Indicators",
      "ui_ages" = "Age Categories",
      "ui_sexes" = "Sex Options",
      "ui_periods" = "Periods"
    )
  )

kable(defaults_df)%>%
  kable_styling() %>%
  column_spec(1, bold = TRUE)

```
</details>
<br><br>

```{r}
deviations_df <- output$deviations_df
deviations_df <- deviations_df %>%
    mutate(
    parameter = recode(
      parameter,
      "ui_country" = "Countries",
      "ui_indicators" = "Indicators",
      "ui_ages" = "Age Categories",
      "ui_sexes" = "Sex Options",
      "ui_periods" = "Periods"
    )
  )
```

<details>
<summary><strong>Which countries deviate from these standard set of input parameters?</strong> Some countries have different parameters options based on available data. <i> `r deviations_df$country` </i>have deviations from the standard set.</summary>

```{r}
kable(deviations_df)  %>%
  kable_styling() %>%
  column_spec(1, bold = TRUE)
```
</details>
<br><br>
```{r}
country_period_df <- output$country_period_df
column_names <- colnames(country_period_df)
columns_with_x <- sapply(country_period_df, function(col) all(col == 'x'))
```
<details>
<summary><strong>For which periods does each country have data?</strong> Periods vary by country ranging from `r column_names[2]` to `r column_names[length(column_names)]`. Every country has data for `r names(columns_with_x[columns_with_x])`. </summary>

```{r}
border_style <- fp_border(color = light_grey, width = 1, style = "solid")
colormatrix <- ifelse(country_period_df[, -1] == "x", midnight_blue, "white")


country_period_ft <- flextable(country_period_df) %>%
  theme_vanilla() %>%
  font(part = "all", fontname = "Source Sans Pro") %>%
  border(border = border_style, part = "all") %>%
  vline(j = 2:ncol(country_period_df), border = border_style) %>% 

  bg(i = 1:nrow(country_period_df), j = 2:ncol(country_period_df), bg = colormatrix) %>%  
  bg(i = 1:nrow(country_period_df), j = 1, bg = light_grey, part = "body") %>%

  add_footer_lines("Countries marked with 'x' indicate participation in the respective periods.") %>%
  bg(part = "header", bg = suva_grey) %>%
  color(part = "header", color = nero) %>%
  color(part = "body", color = nero) %>%
  font(part = "header", fontname = "Source Sans Pro") %>%
  bold(part = "header") %>%
  bold(j = 1, part = "body") %>%
  align(align = "left", part = "all") %>%
  align(align = "left", part = "header") %>%
  align(align = "left", j = 1, part = "body") %>%
  align(align = "center", j = 2:ncol(country_period_df), part = "body") %>%
  set_table_properties(
    x = .,
    opts_html = list(
      scroll = list(
        height = "900px",
        freeze_first_column = TRUE
      )
    )
  )
country_period_ft

```
</details>
<br><br>

<details>
<summary><strong>Find Parameters by Country</strong></summary>

```{r}
# Define the UI
ui <- fluidPage(
  sidebarLayout(
    sidebarPanel(
      width=3,
      selectInput("selected_country", "Select a Country:",
                  choices = unique(parameters_by_country$Country))
    ),
     mainPanel(
      fluidRow(
        width = 9,  # Set the width of the fluid row to 12
        tableOutput("country_parameters")
      )
    )
  )
)

# Define the server
server <- function(input, output) {
  output$country_parameters <- renderTable({
    # Filter the parameters for the selected country
    selected_data <- parameters_by_country %>%
      filter(Country == input$selected_country) %>%
      select(-Country)  # Remove the Country column
    
    # Return the filtered data
    selected_data
  })
}

# Run the app
shinyApp(ui = ui, server = server)

```

</details>
<details>
<summary><strong>View All Parameters by Country</strong></summary>
```{r}
# Create a gt table
kable(parameters_by_country)%>%
  kable_styling() %>%
  column_spec(1, bold = TRUE)

```
</details>

<br><br><br>
